### 2015-02-19 mnsk-2015/thesis.tex
Thesis for mnsk-2015

\documentclass[11pt]{amsart}
\usepackage{latexsym}
\usepackage{amsmath,amsthm,amssymb,amsfonts}
\usepackage[english,russian]{babel}
\usepackage[utf8]{inputenc}

\thispagestyle{empty}

\allowdisplaybreaks

\setlength{\textwidth}{16cm} \setlength{\oddsidemargin}{0.2cm}
\setlength{\evensidemargin}{0.2cm} \setlength{\topmargin}{0.1cm}
\setlength{\footskip}{0.5cm}

\linespread{1}

\renewcommand{\refname}{Bibliography}

\newtheorem{theorem}{Theorem}
\newtheorem{remark}{Remark}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%               Insert here your own definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\RR}{\mathbb{R}}
\newcommand{\NN}{\mathbb{N}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \vspace{0.5cm}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%    Please insert here: first name(s) and surname(s) of the author(s)
%    and the abbreviated addresses of the authors - each abstract should include: 
%    the name of: the University or the Research Institute, City, Country and an email address 
%    of at least one author.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%               Please underline the first name and the surname of the speaker.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

$\blacksquare$ {\bf Долгов Д.А.} {\small email: {\tt 9erthalion6@gmail.com}}, 
{\bf Захаров Ю.Н.}\\

\begin{center}
{\textit {\large Моделирование движения вязкой неоднородной жидкости в крупных кровеносных сосудах}} 
\end{center}

\vspace{0.1 in}

% Underlining the speaker's first name and surname is needed.

  \vspace{0.2 in}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{center} \textbf{Abstract}
%\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%               Insert here your abstract.
%               You can use definitions theorems, etc., if you consider it necessary.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%               Insert here the Bibliography:
% the references in the abstract must be complete i.e.: surname(s) and the initial(s) of first name(s) 
% of the author(s), title, standard abbreviation of journal title, volume, page numbers, year; 
% for a book, year and Publisher as it is below.
%               
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\small  
\begin{thebibliography}{99}

\bibitem{zaharov_miloshevich}
Milosevic H., Gaydarov N. A., Zakharov Y. N., {\textit{Model of incompressible viscous fluid flow driven by  pressure difference in a given channel}}, International Journal of Heat and Mass Transfer, vol. 62, July 2013.

\bibitem{boyce}
Boyce E.G., {\textit{Immersed boundary model of aortic heart valve dynamics with physiological driving and loading conditions}}, International Journal for Numerical Methods in Biomedical Engineering, (2011).

\end{thebibliography}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

>>>>

\documentclass{article}
\usepackage{amsthm,amsfonts,amsmath,amssymb}
\usepackage[utf8]{inputenc}
\usepackage[english, russian]{babel}
\usepackage[final]{graphicx}
\textwidth 11.5cm \textheight 16cm

@@

\begin{flushright}
УДК 519.63    % вставить код УДК, наиболее точно характеризующий работу. См., например, http://pu.virmk.ru/doc/UDK/ 
\end{flushright}

\begin{center}
%НАЗВАНИЕ ДОКЛАДА
\textbf{МОДЕЛИРОВАНИЕ ДВИЖЕНИЯ ВЯЗКОЙ НЕОДНОРОДНОЙ ЖИДКОСТИ В КРУПНЫХ КРОВЕНОСНЫХ СОСУДАХ}
\\
\vspace{\baselineskip}
%АВТОР
Д. А. Долгов
\\
%ВУЗ
Кемеровский государственный университет
\end{center}
\vspace{\baselineskip}
%ТЕКСТ ТЕЗИСА

@@

\noindent\rule{50.0mm}{0.1mm}

\begin{enumerate}
\bibitem{zaharov_miloshevich}               % перед именем ссылки вставляется ФамилияИО докладчика, если несколько работ - то с номером
\textit{H. Milosevic, N.A. Gaydarov, Y.N. Zakharov} Model of incompressible viscous fluid flow driven by  pressure difference in a given channel // International Journal of Heat and Mass Transfer, vol. 62, July 2013.

\bibitem{boyce}
\textit{E.G. Boyce} Immersed boundary model of aortic heart valve dynamics with physiological driving and loading conditions // International Journal for Numerical Methods in Biomedical Engineering, (2011).
\end{enumerate}

\begin{flushright}
\textbf{\textit{Научный руководитель --- д-р физ.-мат. наук, проф.
Ю.Н.~Захаров}}

\end{flushright}
\end{document}
